\begin{titlepage}
%\BgThispage
%\newgeometry{left=1cm,right=4cm}
\vspace*{0.5cm}
\noindent

\begin{flushleft}
\textcolor{darkgray}{\LARGE Forward}
\vspace*{1cm}\par

This document, designed for experienced users, includes advanced knowledge, features, and skills of GSI as well as details of assimilation of specific data types. Users may use as a reference for their special research topics. To read this guide, users should already read and understand the content in the GSI User\textquotesingle s Guide. 

This version of Advanced GSI User\textquotesingle s Guide was first released with the community GSI version 3.3 in 2014. Please note, not like the basic GSI user\textquotesingle s guide which is being updated every year and closely follows the GSI release code, this advanced user\textquotesingle s guide, as a reference, is only being updated as needed and therefore does not pertain to one specific code release. 

This Advanced User\textquotesingle s Guide consists of ten chapters:
\begin{description}
\item[Chapter 1] Overview
\item[Chapter 2] Software Installation
\item[Chapter 3] Advanced Topics on Run and Diagnosis 
\item[Chapter 4] GSI Theory 
\item[Chapter 5] GSI Code Structure 
\item[Chapter 6] Static Background Error Covariance 
\item[Chapter 7] Observations 
\item[Chapter 8] Satellite Radiance Data Assimilation 
\item[Chapter 9] Radar Data Assimilation 
\item[Chapter 10] GSI Applications
\end{description}

DTC will update the content of this advanced User\textquotesingle s Guide if needed after the release. For the latest version of this document, please visit the GSI User\textquotesingle s Website at

\url{http://www.dtcenter.org/com-GSI/users/index.php}

Please send questions and comments to:
\begin{center}
gsi-help@ucar.edu
\end{center}

For referencing this document, please use:
\texttt{Developmental Testbed Center, 2016: Gridpoint Statistical Interpolation Advanced User\textquotesingle s Guide Version 3.5.0.0. Available at http://www.dtcenter.org/com-GSI/users/docs/index.php, 119 pp.}

For referencing the general aspect of the GSI community effort, please use: 
\texttt{Shao, H., J. Derber, X.-Y. Huang, M. Hu, K. Newman, D. Stark, M. Lueken, C. Zhou, L. Nance, Y.-H. Kuo, B. Brown, 2016:  Bridging Research to Operations Transitions:  Status and Plans of Community GSI. Bulletin of the American Meteorological Society, doi:10.1175/BAMS-D-13-00245.1, in press}

\end{flushleft}
\end{titlepage}
\pagebreak{}




